---
title: "Project1-Group2"
author: "Emma Zhang, Ricky Wong, Xiaoxin Bian"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
  word_document: default
runtime: shiny
---

## Objective

The goal of this project is to conduct a sentiment analysis of popular keywords and phrases across Twitter, Instagram, and Facebook. This analysis aims to uncover and understand public opinions and emotions, providing actionable insights that enable Ignite Digital, a digital marketing agency, to refine their strategies and enhance their service offerings.

## Install required libraries

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#install.packages("shiny")
#install.packages("shinydashboard")
#install.packages("dplyr")
#install.packages("ggplot2")
#install.packages("stringr")
#install.packages("wordcloud")
#install.packages("RColorBrewer")
#install.packages("tm")
#install.packages("tidytext")
```

```{r, include=FALSE}
library(shiny)
library(shinydashboard)
library(dplyr)
library(ggplot2)
library(stringr)
library(wordcloud)
library(RColorBrewer)
library(tm)
library(tidytext)
```

## Load the dataset

```{r, include = TRUE, echo = TRUE}
df <- read.csv("./sentimentdataset.csv")
```

**Use glimpse to explore the dataset.**

```{r, include = TRUE, echo = TRUE}
glimpse(df)
```

## Data Processing

**Remove unnecessary columns**

```{r, include = TRUE, echo = TRUE}
df <- df[, -c(1, 2)]
df$Country <- as.factor(str_trim(df$Country))
```

**Define sentiment label categories**

```{r, include = TRUE, echo = TRUE}
positive <- c("Positive", "Happiness", "Joy", "Love", "Amusement", "Enjoyment", "Admiration", "Affection", "Awe","Acceptance", "Adoration", "Calmness", "Excitement", "Kind", "Pride", "Elation", "Euphoria", "Contentment", "Serenity", "Gratitude", "Hope", "Empowerment", "Compassion", "Tenderness", "Enthusiasm", "Fulfillment", "Reverence", "Hopeful", "Proud", "Grateful", "Empathetic", "Compassionate", "Playful", "Free-spirited", "Inspired", "Confident", "Thrill", "Overjoyed", "Inspiration", "Motivation", "JoyfulReunion","Satisfaction", "Blessed", "Appreciation", "Confidence", "Accomplishment", "Wonderment", "Optimism", "Enchantment", "Mindfulness", "Elegance", "Whimsy", "Harmony", "Creativity", "Radiance", "Wonder", "Rejuvenation", "Coziness", "Adventure", "Melodic", "FestiveJoy", "InnerJourney", "Freedom", "Dazzle", "Adrenaline", "ArtisticBurst", "CulinaryOdyssey", "Resilience", "Immersion", "Spark", "Marvel", "Positivity", "Kindness", "Friendship", "Success", "Exploration", "Amazement", "Romance", "Captivation", "Tranquility", "Grandeur", "Emotion", "Energy", "Celebration", "Charm", "Ecstasy", "Colorful", "Hypnotic", "Connection", "Iconic", "Journey", "Engagement", "Touched", "Triumph", "Heartwarming", "Solace", "Breakthrough", "Imagination", "Vibrancy", "Mesmerizing", "Creative Inspiration", "Nature's Beauty", "Celestial Wonder", "Happy", "PlayfulJoy", "DreamChaser", "Blessing", "Sympathy", "Renewed Effort", "Culinary Adventure", "Determination", "Zest", "Joy in Baking", "Challenge", "Winter Magic", "Thrilling Journey", "Runway Creativity", "Ocean's Freedom", "Relief", "Curiosity"
)

negative <- c("Negative", "Anger", "Fear", "Sadness", "Disgust", "Disappointed", "Bitter", "Shame", "Despair", "Grief", "Loneliness", "Jealousy", "Resentment", "Frustration", "Boredom", "Anxiety", "Intimidation", "Helplessness", "Envy", "Regret", "Melancholy", "Fearful", "Apprehensive", "Overwhelmed", "Devastated", "Frustrated", "Envious", "Dismissive", "Bitterness", "Heartbreak", "Betrayal", "Suffering", "EmotionalStorm", "Isolation", "Disappointment", "LostLove", "Exhaustion", "Sorrow", "Darkness", "Desperation", "Ruins", "Desolation", "Loss", "Heartache", "Solitude", "Obstacle", "Pressure", "Miscalculation", "Sad", "Hate", "Bad", "Jealous", "Embarrassed"
)

neutral <- c("Neutral", "Surprise", "Anticipation", "Confusion", "Arousal", "Indifference", "Numbness", "Nostalgia", "Ambivalence",  "Contemplation", "Reflection", "Intrigue", "Whispers of the Past", "Pensive", "Bittersweet", "Suspense", "Envisioning History", "Mischievous", "Yearning"
)

```

**Add a label column based on category definition**

```{r, include = TRUE, echo = TRUE}
df <- df %>% mutate(
  Sentiment = trimws(Sentiment),
  Sentiment_Label = case_when(
  Sentiment %in% positive ~ "Positive",
  Sentiment %in% negative ~ "Negative",
  Sentiment %in% neutral ~ "Neutral"
))
```

\*\*View processed data\*

```{r, include = TRUE, echo = TRUE}
head(df)
```

\*\*Sentiment distribution by platform\*

```{r, include = TRUE, echo = TRUE}
sentiment_platform <- df %>%
  mutate(Platform = trimws(Platform)) %>% 
  group_by(Platform, Sentiment_Label) %>%
  summarise(Count = n())

sentiment_platform
```

```{r}
# Extract hashtags from the Hashtags column
extract_hashtags <- function(hashtags) {
  unlist(strsplit(hashtags, " "))
}

all_hashtags <- unlist(lapply(df$Hashtags, extract_hashtags))
all_hashtags <- all_hashtags[all_hashtags != "" & all_hashtags != " "]
hashtag_counts <- as.data.frame(table(all_hashtags))

colnames(hashtag_counts) <- c("Hashtag", "Frequency")
sorted_hashtag_counts <- hashtag_counts %>%
  arrange(desc(Frequency))

sorted_hashtag_counts
```

## Question 1: What are the prevailing sentiments associated with key marketing terms and how do they vary across different social media platforms?

Authored by: Emma Zhang

```{r, include = TRUE, echo = TRUE}
library(ggplot2)
ggplot(sentiment_platform, aes(x = trimws(Platform), y = Count, fill = Sentiment_Label)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Sentiment Distribution by Platform", x = "Platform", y = "Count")
```

## Question 2: How do public sentiments correlate with variations in engagement metrics like likes and retweets?

Authored by: Emma Zhang

```{r, include = TRUE, echo = TRUE}
ggplot(df, aes(x = Sentiment_Label, y = Likes, fill = Sentiment_Label)) +
  geom_boxplot() +
  labs(title = "Box Plot of Likes by Sentiment", x = "Sentiment", y = "Likes")

ggplot(df, aes(x = Sentiment_Label, y = Retweets, fill = Sentiment_Label)) +
  geom_boxplot() +
  labs(title = "Box Plot of Retweets by Sentiment", x = "Sentiment", y = "Retweets")
```

## Question 3:

Authored by: Xiaoxin Bian

```{r}
```

## Question 4:

Authored by: Xiaoxin Bian

```{r}
```

## Question 5: How do the sentiments associated with key marketing terms change over time? Which months have the highest counts of positive and negative sentiments, and what are the trending hashtags during these periods? [Temporal Trends Strategy]

Authored by: Ricky Wong

In marketing trend investigations, understanding regional differences in user-generated content is crucial for tailoring strategies to specific markets. Social media users come from diverse regions, and analyzing sentiment and engagement metrics across these regions helps us optimize our marketing efforts.

By examining our dataset, which categorizes user-generated content by sentiment (positive, negative, neutral) and includes engagement metrics like likes and retweets, we can identify regional trends. This analysis focuses on North America and Europe to highlight key differences.

Analysis Strategy:
1. We grouped the data by country and sentiment to observe variations. We focused on the top 10 countries by post count, calculating the percentage of each sentiment.
2. We want to focus in North America and Europe, we grouped the top 10 countries into North America and Europe. We then again analyze sentiment distribution within these regions.
3. For each region, identify the top 10 hashtags based on the total number of retweets from posts containing these hashtags.

```{r}
sentiment_by_region <- df %>%
  group_by(Country, Sentiment_Label) %>%
  summarize(count = n()) %>%
  ungroup()

top_countries <- sentiment_by_region %>%
  group_by(Country) %>%
  summarize(total_count = sum(count)) %>%
  top_n(10, total_count) %>%
  pull(Country)

top_sentiment_by_region <- sentiment_by_region %>%
  filter(Country %in% top_countries)

top_sentiment_by_region <- top_sentiment_by_region %>%
  group_by(Country) %>%
  mutate(percentage = count / sum(count) * 100) %>%
  ungroup()

top_sentiment_by_region <- top_sentiment_by_region %>%
  left_join(
    sentiment_by_region %>%
      group_by(Country) %>%
      summarize(total_count = sum(count)),
    by = "Country"
  )

top_sentiment_by_region

p1 <- ggplot(top_sentiment_by_region, aes(x = reorder(Country, total_count), y = count, fill = Sentiment_Label)) +
  geom_bar(stat = "identity", position = "stack") +
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), size = 3) +
  ggtitle("Sentiment Distribution Across Top 10 Regions") +
  theme_minimal() +
  xlab("Country") +
  ylab("Count") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        plot.title = element_text(hjust = 0.5),
        legend.position = "top") +
  theme(plot.margin = margin(5, 5, 5, 5),
        plot.background = element_rect(fill = "white"),
        panel.background = element_rect(fill = "white")) +
  theme(plot.margin = unit(c(1, 1, 1, 1), "cm")) +
  coord_flip() +
  theme(plot.background = element_rect(fill = "white"),
        panel.background = element_rect(fill = "white")) +
  theme(plot.margin = unit(c(1, 1, 1, 1), "cm"))

p1

# ggsave("./charts/sentiment_distribution_across_regions.png", p1, height = 15, width =25)
```

### Results 1

From the analysis, it is observed that the USA has the highest number of posts. Among these posts, approximately 70% express a positive sentiment, which is the highest compared to the other nine countries. In the top 10 countries, North America includes the USA and Canada, while European countries include the UK, France, Germany, and Italy.

```{r}
north_america <- c("USA", "Canada")
europe <- c("UK", "Germany", "France", "Italy")

df_na <- df %>% filter(Country %in% north_america)
df_eu <- df %>% filter(Country %in% europe)

# Top 10 hashtags by retweets in North America
top_hashtags_na <- df_na %>%
  filter(Sentiment == "Positive") %>%
  unnest_tokens(word, Hashtags) %>%
  group_by(word) %>%
  summarize(total_retweets = sum(Retweets)) %>%
  top_n(10, total_retweets)

# Top 10 hashtags by retweets in Europe
top_hashtags_eu <- df_eu %>%
  filter(Sentiment == "Positive") %>%
  unnest_tokens(word, Hashtags) %>%
  group_by(word) %>%
  summarize(total_retweets = sum(Retweets)) %>%
  top_n(10, total_retweets)

# Plot top hashtags by retweets for North America
p2 <- ggplot(top_hashtags_na, aes(x = reorder(word, total_retweets), y = total_retweets)) +
  geom_bar(stat = "identity", fill = "blue") +
  coord_flip() +
  ggtitle("Top 10 Hashtags by Retweets in North America") +
  xlab("Hashtag") +
  ylab("Total Retweets")

print(p2)

# Plot top hashtags by retweets for Europe
p3 <- ggplot(top_hashtags_eu, aes(x = reorder(word, total_retweets), y = total_retweets)) +
  geom_bar(stat = "identity", fill = "red") +
  coord_flip() +
  ggtitle("Top 10 Hashtags by Retweets in Europe") +
  xlab("Hashtag") +
  ylab("Total Retweets")

print(p3)
```

```{r}
# Select top 3 hashtags from the top 10

# Create word clouds for top 3 hashtags
wordcloud(words = top_hashtags_na$word, freq = top_hashtags_na$total_retweets, 
          scale = c(2, 0.1), min.freq = 1, 
          max.words = 200, 
          random.order = FALSE, 
          rot.per = 0.35,colors = brewer.pal(8, "Blues"), main = "Top 3 Hashtags in North America")

wordcloud(words = top_hashtags_eu$word, freq = top_hashtags_eu$total_retweets, 
          scale = c(2, 0.1), min.freq = 1, 
          max.words = 200, 
          random.order = FALSE, 
          rot.per = 0.35,colors = brewer.pal(8, "Oranges"), main = "Top 3 Hashtags in Europe")
```

### Results 2

We aggregated the data according to the countries belonging to North America and Europe and further analyzed it. We identified the top 10 hashtags by retweets in both regions. For North America, the top hashtags are #cooking, #workfromhome, #productivity, #coding, and so on. For Europe, the leading hashtags are #fitnesschallenge, #familytime, #weekend, and #newbeginnings.

### Insight

Understanding these regional differences allows us to:

- tailor content to fit the preferences and sentiments of each region, improving engagement and conversion rates. For example, ...
- use sentiment and hashtag trends to create targeted marketing campaigns, such as leveraging nostalgic content in regions where it performs well. For example, ...

## Question 6: How do the sentiments associated with key marketing terms change over time? Which months have the highest counts of positive and negative sentiments, and what are the trending hashtags during these periods? [Time-specifc strategy]

Authored by: Ricky Wong

```{r}
df$Timestamp <- as.POSIXct(df$Timestamp, format="%Y-%m-%d %H:%M:%S")

# Extract year and month for time series analysis
df <- df %>%
  mutate(YearMonth = format(Timestamp, "%Y-%m"))

# Filter data to include only from 2020 onward
df <- df %>%
  filter(format(Timestamp, "%Y") >= 2020)

# Group by YearMonth and Sentiment to get the count of each sentiment per month
sentiment_over_time <- df %>%
  group_by(YearMonth, Sentiment_Label) %>%
  summarize(count = n()) %>%
  ungroup()

sentiment_over_time

# Plot the sentiment trends over time
ggplot(sentiment_over_time, aes(x = as.Date(paste0(YearMonth, "-01")), y = count, color = Sentiment_Label)) +
  geom_line(size = 1) +
  geom_point(size = 2) +
  ggtitle("Sentiment Trends Over Time From 2020") +
  xlab("Time") +
  ylab("Count of Sentiments") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

```{r}
max_positive_month <- sentiment_over_time %>%
  filter(Sentiment_Label == "Positive") %>%
  arrange(desc(count)) %>%
  slice(1) %>%
  pull(YearMonth)

max_negative_month <- sentiment_over_time %>%
  filter(Sentiment_Label == "Negative") %>%
  arrange(desc(count)) %>%
  slice(1) %>%
  pull(YearMonth)

positive_month_data <- df %>%
  filter(YearMonth == max_positive_month)

negative_month_data <- df %>%
  filter(YearMonth == max_negative_month)

top_positive_hashtags <- positive_month_data %>%
  unnest_tokens(word, Hashtags) %>%
  group_by(word) %>%
  summarize(post_count = n()) %>%
  arrange(desc(post_count))

top_negative_hashtags <- negative_month_data %>%
  unnest_tokens(word, Hashtags) %>%
  group_by(word) %>%
  summarize(post_count = n()) %>%
  arrange(desc(post_count))

top_positive_hashtags
top_negative_hashtags

wordcloud(words = top_positive_hashtags$word, freq = top_positive_hashtags$post_count, 
          scale = c(2, 0.1), min.freq = 1, 
          max.words = 200, 
          random.order = FALSE, 
          rot.per = 0.35, colors = brewer.pal(8, "Blues"), main = paste("Top Hashtags in", max_positive_month, "(Positive)"))

wordcloud(words = top_negative_hashtags$word, freq = top_negative_hashtags$post_count, 
          scale = c(2, 0.1), min.freq = 1, 
          max.words = 200, 
          random.order = FALSE, 
          rot.per = 0.35, colors = brewer.pal(8, "Reds"), main = paste("Top Hashtags in", max_negative_month, "(Negative)"))


```

### Results

From the analysis, we observed that the months with the highest counts of positive and negative sentiments vary. Specifically, January 2023 had the highest count of positive sentiment, while September 2023 had the highest count of negative sentiment.

For the month with the highest positive sentiment, the top hashtags included:

- #cooking
- #nature
- #gaming
- #fitness

For the month with the highest negative sentiment, the top hashtags included:

- #highschoolstruggles
- #highschoolreality
- #highschoolemotions

This pattern is quite reasonable and understandable. January, being the start of the year, is a time when people tend to stay positive and motivated, setting new goals. On the other hand, September marks the beginning of a new academic year. Adolescents face new challenges and uncertainties, especially those entering high school, which can lead to feelings of pessimism or negativity.

### Insight

Understanding these temporal sentiment trends enables Ignite Digital to tailor their marketing strategies more effectively. For example, promoting wellness and self-improvement content in January or addressing back-to-school anxieties in September can lead to more impactful and timely marketing efforts. By aligningour campaigns with the flow of public sentiment, we can enhance engagement and resonance with our audience.


## Shiny Dashboard

```{r}
ui <- dashboardPage(
  dashboardHeader(title = "Sentiment Analysis Dashboard"),
  dashboardSidebar(
    sidebarMenu(
      menuItem("Sentiment Distribution", tabName = "sentiment", icon = icon("chart-bar")),
      menuItem("Top Hashtags", tabName = "hashtags", icon = icon("hashtag"))
    )
  ),
  dashboardBody(
    tabItems(
      # First tab content
      tabItem(tabName = "sentiment",
              fluidRow(
                box(
                  title = "Sentiment Distribution Across Top 10 Regions", status = "primary", solidHeader = TRUE, collapsible = TRUE,
                  plotOutput("sentimentPlot", width = 1200)
                , width=12)
              )
      ),
      
      # Second tab content
      tabItem(tabName = "hashtags",
              fluidRow(
                box(
                  title = "Top 10 Hashtags by Retweets", status = "primary", solidHeader = TRUE, collapsible = TRUE,
                  selectInput("region", "Select Region:", choices = c("North America", "Europe")),
                  plotOutput("hashtagPlot", height = 400)
                )
              ),
              fluidRow(
                box(
                  title = "Word Cloud of Top 3 Hashtags", status = "primary", solidHeader = TRUE, collapsible = TRUE,
                  plotOutput("wordcloudPlot", height = 400)
                )
              )
      )
    )
  )
)

# Define server logic required
server <- function(input, output) {
  
  # Preprocess data for sentiment analysis
  sentiment_by_region <- df %>%
    group_by(Country, Sentiment_Label) %>%
    summarize(count = n()) %>%
    ungroup()
  
  top_countries <- sentiment_by_region %>%
    group_by(Country) %>%
    summarize(total_count = sum(count)) %>%
    top_n(10, total_count) %>%
    pull(Country)
  
  
  # Render sentiment distribution plot
  output$sentimentPlot <- renderPlot({
    ggplot(top_sentiment_by_region, aes(x = reorder(Country, total_count), y = count, fill = Sentiment_Label)) +
      geom_bar(stat = "identity", position = "stack") +
      geom_text(aes(label = paste0(round(percentage, 1), "%")), 
                position = position_stack(vjust = 0.5), size = 3) +
      ggtitle("Sentiment Distribution Across Top 10 Regions") +
      theme_minimal() +
      xlab("Country") +
      ylab("Count") +
      theme(axis.text.x = element_text(angle = 45, hjust = 1),
            plot.title = element_text(hjust = 0.5),
            legend.position = "top") +
      coord_flip()
  })
  
  # Reactive expressions for region-specific data
  north_america <- c("USA", "Canada")
  europe <- c("UK", "Germany", "France", "Italy")
  
  region_data <- reactive({
    if (input$region == "North America") {
      df %>% filter(Country %in% north_america)
    } else {
      df %>% filter(Country %in% europe)
    }
  })
  
  # Render hashtag plot based on selected region
  output$hashtagPlot <- renderPlot({
    data <- region_data()
    
    top_hashtags <- data %>%
      filter(Sentiment == "Positive") %>%
      unnest_tokens(word, Hashtags) %>%
      group_by(word) %>%
      summarize(total_retweets = sum(Retweets)) %>%
      top_n(10, total_retweets)
    
    ggplot(top_hashtags, aes(x = reorder(word, total_retweets), y = total_retweets)) +
      geom_bar(stat = "identity", fill = ifelse(input$region == "North America", "blue", "red")) +
      coord_flip() +
      ggtitle(paste("Top 10 Hashtags by Retweets in", input$region)) +
      xlab("Hashtag") +
      ylab("Total Retweets")
  })
  
  # Render word cloud based on selected region
  output$wordcloudPlot <- renderPlot({
    data <- region_data()
    
    top_hashtags <- data %>%
      filter(Sentiment == "Positive") %>%
      unnest_tokens(word, Hashtags) %>%
      group_by(word) %>%
      summarize(total_retweets = sum(Retweets)) %>%
      top_n(10, total_retweets)
    
    top_3_hashtags <- top_hashtags %>%
      top_n(3, total_retweets)
    
    wordcloud(words = top_3_hashtags$word, freq = top_3_hashtags$total_retweets, 
              scale = c(3, 0.5), colors = ifelse(input$region == "North America", "blue", "red"))
  })
}

# Run the application 
shinyApp(ui = ui, server = server)
```
